Tables in the project

### 2018-08-01 paper/Chapters/Chapter2.tex
tables replaced with time slots versions

If the day-level LCA model (carbohydrate eating pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model. Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout 4 consecutive days of survey period). Considering the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-0.8cm}

@@

Another approach is using a non-parametric MLCA, in which separate latent class models are specified for level 1 and level 2. Similar with the parametric MLCA approach, there are $T-1$ random intercepts, where $T$ is the number of level 1 latent classes. However, rather than assuming the random intercepts following a normal distribution, the non-parametric MLCA assumes a multinomial (discrete) distribution of the level 2 latent classes. This approach is less computationally demanding compared with the parametric approach. These level 2 latent
classes reflect differences in the probability of belonging to a specific level 1 latent class, so that clusters (i.e., individuals) that contain observations with similar probabilities for the level 1 latent classes will be grouped together. The non-parametric MLCA model can be defined as follows: \vspace{-0.7cm}

@@

\begin{itemize}
	\item $CB_j$ is level 2 latent class membership for $j$th individual;
	\item $\gamma_{tm}$ is level 1 and level 2 indicators. 
\end{itemize}

According to Finch and French's simulation study \parencite{finch2014multilevel}, non-parametric approach generally resulted in more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model. Specifically, we are interested in exploring meaningful individual (level 2) latent classes rather than their daily consumption classification. Therefore, non-parametric MLCA was employed 1) to identify latent classes of observations (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.\vspace{-0.3cm}

@@

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2. \vspace{-0.3cm}

@@

\section{Association between latent classes and other variables}\vspace{-0.3cm}

>>>>

If the day-level LCA model (carbohydrate eating pattern typologies) is best defined by $T (T \geqslant 2)$ latent classes, then $T-1$ random intercept will be specified by a two-level multinomial logistic regression model. Similar to the typical LCA models, the latent class variable in a MLCA is defined by multiple observed indicators (here is defined by the responses of eating carbohydrate within each time slots, throughout 4 consecutive days of survey period). Considering the latent class indicators are indicator variables ($U_{ijk}$), the MLCA model can be written as follows:\vspace{-1cm}

@@

Since the parametric approach discussed above can be extremely computationally demanding \parencite{van2008using, vermunt2008latent}, an alternative approach is using a non-parametric MLCA \parencite{davidian2008growth}. In this approach, separate latent class models are specified for level 1 (observation days) and level 2 (individuals). Similar with the parametric MLCA approach, there are $T-1$ random intercepts, where $T$ is the number of level 1 latent classes. However, rather than assuming the random intercepts following a normal distribution, the non-parametric MLCA assumes a multinomial (discrete) distribution of the level 2 latent classes. This approach is less computationally demanding compared with the parametric approach. These level 2 (individual) latent classes reflect differences in the probability of belonging to a specific day-level latent class, so that individuals that contain observation days with similar probabilities for the level 1 latent classes will be grouped together. The non-parametric MLCA model can be defined as follows: \vspace{-0.7cm}

@@

\begin{itemize}
	\item $CB_j$ is individual-level latent class membership for $j$th individual;
	\item $\gamma_{tm}$ is day-level and individual-level indicators. 
\end{itemize}

According to Finch and French's simulation study \parencite{finch2014multilevel}, non-parametric approach generally resulted in more accurate recovery of the underlying latent structure of the data at both levels and provided better latent class model. Specifically, we are interested in exploring both meaningful individual (level 2) latent classes and the daily carbohydrate consumption classification. Therefore, non-parametric MLCA was employed 1) to identify latent classes of observation days (level 1) based on the subjects' responses to the 4-day food and drink diary and 2) to form distinct latent classes of individuals (level 2) based on the distribution of observation-level latent classes within individuals.\vspace{-0.3cm}

@@

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where LMR-LRT is available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in observation day-level and individual-level. MLCA models were fitted in Mplus 7.4 \parencite{muthen2005mplus}, the Mplus codes are shown in the Appendix xxx. \vspace{-0.3cm}

@@

\section{Association between day-level and individual-level latent classes and other variables}\vspace{-0.3cm}

Day-level latent classes identified by MLCA steps were tabulated according to whether the diary was recorded during weekdays or not. A contingency table giving the frequency of responses across the 7 time slots of the survey days was produced.

### 2018-08-01 paper/Chapters/Chapter3.tex
tables replaced with time slots versions

\section{Main Section 1}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

@@

>>>>

\section{Model selection, comparison, and interpretation}

%
%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
%\subsection{Subsection 1}

\rowcolors{2}{gray!6}{white}

\begin{table}[H]

	\caption{\label{tab:mixmodels}Fit Criteria for Each Model Specification}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Number of day-level classes}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{1 class} & \textbf{2 classes} & \textbf{3 classes} & \textbf{4 classes} & \textbf{5 classes}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
		\hspace{1em}No. of free parameters & 14 & 29 & 44 & 59 & 74\\
		\hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
		\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
		\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & $<$ 0.0001 & 1e-04 & $<$ 0.0001 & $<$ 0.0001\\
		\hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Random effects model}}\\
		\hspace{1em}2 individual-level classes &  &  &  &  & \\
		\hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
		\hspace{1em}\hspace{1em}Log-likelihood &  & -169331.132 & -168700.96 & -168366.193 & \\
		\hspace{1em}\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
		\hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
		\hspace{1em}3 individual-level classes &  &  &  &  & \\
		\hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
		\hspace{1em}\hspace{1em}Log-likelihood &  & -166936.279 & -166348.815 & -166062.761 & \\
		\hspace{1em}\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
		\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
		\hspace{1em}4 individual-level classes &  &  &  &  & \\
		\hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
		\hspace{1em}\hspace{1em}Log-likelihood &  & -165441.731 & -164845.696 &  & \\
		\hspace{1em}\hspace{1em}BIC &  & 332086.045 & 331500.318 &  & \\
		\hspace{1em}\hspace{1em}Entropy &  & 0.729 & 0.659 &  & \\
		\bottomrule
		\multicolumn{6}{l}{\textit{Note: }}\\
		\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index;}\\ 
		\multicolumn{6}{l}{Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
	\end{tabular}
\end{table}

\rowcolors{2}{white}{white}

\rowcolors{2}{gray!6}{white}

\begin{table}

	\caption{\label{tab:daylevel}Day Level Latent Class Solution for Three-Class Model (No Individual level Model)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{llccccc}
		\hiderowcolors
		\toprule
		\textbf{Time slots of} & \textbf{Responses of} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(30.8\%)}} & \textbf{\Centerstack{Class 2\\(39.8\%)}} & \textbf{\Centerstack{Class 3\\(29.5\%)}} \\
		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Lower carbo-\\hydrate day}} & \textbf{Regular day}\\
		\midrule
		\showrowcolors
		6 am – 9 am &  &  &  &  &  & \\
		& Not eating & 7655 & 31.2 & 0.129 & 0.45 & 0.32\\
		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.13 & 0.267 & 0.128\\
		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
		9 am – 12 am &  &  &  &  &  & \\
		& Not eating & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
		12 noon – 2 pm &  &  &  &  &  & \\
		& Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.56\\
		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
		2 pm – 5 pm &  &  &  &  &  & \\
		& Not eating & 6926 & 28.3 & 0.13 & 0.123 & 0.659\\
		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
		5 pm – 8 pm &  &  &  &  &  & \\
		& Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.59 & 0.639\\
		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.37 & 0.211 & 0.328\\
		8 pm – 10 pm &  &  &  &  &  & \\
		& Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.48\\
		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
		10 pm – 6 am &  &  &  &  &  & \\
		& Not eating & 16295 & 66.6 & 0.68 & 0.59 & 0.751\\
		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
		\bottomrule
		\multicolumn{7}{l}{\textit{Note: }}\\
		\multicolumn{7}{l}{\textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed less }\\
		\multicolumn{7}{l}{than 50\% total energy intake.}\\ 
		\multicolumn{7}{l}{\textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed higher }\\
		\multicolumn{7}{l}{or equal to 50\% total energy intake.}\\ 
	\end{tabular}
\end{table}

\rowcolors{2}{white}{white}

@@

%
%\rowcolors{2}{gray!6}{white}
%
%\begin{table}
%	
%	\caption{\label{tab:LCGAtab1}Means, percentages, and 95\% CIs of the characteristics of carbohydrate temporal eating patterns by LCGA memberships in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}\vspace{-0.3cm}
%	\centering
%	\fontsize{9}{11}\selectfont
%	\begin{tabular}[t]{lcccc}
%		\hiderowcolors
%		\toprule
%		 & Latent class = 1 & Latent class = 2 & Latent class = 3 & P value \textsuperscript{*}\\
%		\midrule
%		\showrowcolors
%		Total (\%) & 28.4 (26.8, 30.1) & 7.0 (6.2, 7.9) & 64.6 (62.9, 66.2) & \\
%		Countries (\%) &  &  &  & \\
%		\hspace{1em}England & 81.4 (78.5, 84.0) & 87.5 (82.9, 91.0) & 84.6 (82.5, 86.4) & 0.004\\
%		\hspace{1em}Northern Ireland & 3.9 (2.9, 5.1) & 0.6 (0.3, 1.2) & 2.5 (2.0, 3.2) & \\
%		\hspace{1em}Scotland & 9.5 (7.4, 12.3) & 6.2 (3.5, 10.6) & 8.3 (6.7, 10.3) & \\
%		\hspace{1em}Wales & 5.2 (4.1, 6.6) & 5.7 (3.8, 8.5) & 4.6 (3.8, 5.6) & \\
%		Age (years) & 43.8 (42.4, 45.1) & 49.1 (47.2, 50.9) & 50.1 (49.3, 50.9) & $<$ 0.001\\
%		Sex (\%) &  &  &  & \\
%		\hspace{1em}Men & 50.6 (47.3, 53.9) & 49.6 (43.7, 55.4) & 47.6 (45.4, 49.7) & 0.273\\
%		\hspace{1em}Women & 49.4 (46.1, 52.7) & 50.4 (44.6, 56.3) & 52.4 (50.3, 54.6) & \\
%		Survey years (\%) &  &  &  & \\
%		\hspace{1em}1 & 11.4 (8.8, 14.7) & 17.1 (12.4, 23.3) & 14.4 (11.9, 17.4) & 0.002\\
%		\hspace{1em}2 & 10.1 (7.8, 13.1) & 18.3 (13.3, 24.7) & 12.4 (10.2, 15.0) & \\
%		\hspace{1em}3 & 13.9 (10.8, 17.7) & 9.1 (5.7, 14.1) & 10.7 (8.6, 13.1) & \\
%		\hspace{1em}4 & 10.9 (8.5, 13.9) & 13.8 (9.7, 19.4) & 13.2 (10.9, 16.0) & \\
%		\hspace{1em}5 & 13.5 (10.6, 17.0) & 12.8 (8.4, 19.1) & 13.3 (11.0, 16.1) & \\
%		\hspace{1em}6 & 12.8 (10.1, 16.1) & 8.7 (5.7, 12.9) & 11.5 (9.5, 13.9) & \\
%		\hspace{1em}7 & 14.3 (11.5, 17.6) & 9.5 (6.5, 13.8) & 12.4 (10.2, 15.0) & \\
%		\hspace{1em}8 & 13.2 (10.5, 16.4) & 10.5 (7.4, 14.8) & 12.1 (9.9, 14.6) & \\
%		BMI (kg/m\textasciicircum{}2) & 27.5 (27.1, 27.9) & 27.0 (26.4, 27.6) & 27.4 (27.2, 27.6) & 0.433\\
%		WC (cm) & 93.3 (92.1, 94.5) & 92.9 (90.9, 95.0) & 93.1 (92.3, 93.8) & 0.928\\
%		Smoking status (\%) &  &  &  & \\
%		\hspace{1em}Current & 24.1 (21.5, 27.0) & 30.0 (24.8, 35.8) & 18.8 (17.2, 20.6) & $<$ 0.001\\
%		\hspace{1em}Ex-smoker & 20.0 (17.6, 22.6) & 27.5 (22.4, 33.2) & 25.9 (24.1, 27.7) & \\
%		\hspace{1em}Never & 55.9 (52.7, 59.0) & 42.5 (36.6, 48.7) & 55.3 (53.2, 57.4) & \\
%		Current drinking status (\%) &  &  &  & \\
%		\hspace{1em}Yes & 24.6 (21.7, 27.7) & 18.3 (14.0, 23.6) & 16.8 (15.3, 18.4) & $<$ 0.001\\
%		Hypertension (\%) \textsuperscript{\dag} &  &  &  & \\
%		\hspace{1em}Yes & 25.9 (22.3, 29.9) & 31.8 (25.3, 39.1) & 30.4 (27.9 32.8) & 0.111\\
%		Total energy intake (KJ) &  \Centerstack{ 6713.8 \\ (6575.7, 6851.8)}   &  \Centerstack{ 9256.0 \\ (8850.8, 9661.2)}   &  \Centerstack{7916.9 \\ (7814.0, 8019.9)}     & $<$ 0.001\\
%		Carbohydrate intake (g) & 192.9 (188.5, 197.3) & 275.6 (263.4, 287.8) & 226.9 (223.9, 229.9) & $<$ 0.001\\
%		Carbohydrate
%		percent (\%) \textsuperscript{\ddag} & 45.8 (45.3, 46.4) & 47.4 (46.5, 48.3) & 45.6 (45.3, 45.9) & 0.001\\
%		Glucose (mmol/l) & 5.16 (5.08, 5.23) & 5.09 (5.00, 5.18) & 5.14 (5.10, 5.19) & 0.537\\
%		A1C (\%) & 5.47 (5.42, 5.51) & 5.48 (5.42, 5.54) & 5.49 (5.47. 5.52) & 0.403\\
%		DM \textsuperscript{\S} & 5.9 (4.2, 8.2) & 1.1 (0.2, 5.2) & 4.7 (3.6, 6.0) & 0.053\\
%        Physical activity (hs/day) \textsuperscript{\P}& 1.31 (1.14, 1.49) & 1.82 (1.44, 2.19) & 1.62 (1.49, 1.76) & 0.018\\
%		\bottomrule
%		\multicolumn{5}{l}{\textit{Note: }}\\
%		\multicolumn{5}{l}{\textbf{Abbreviations}: CI, confidence intervals; LCGA, latent class growth analysis; NDNS RP, national}\\ 
%		\multicolumn{5}{l}{dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference; }\\
%		\multicolumn{5}{l}{A1C, haemoglobin A1c;DM, diabetes mellitus; h, hour.}\\
%		\multicolumn{5}{l}{Variables from the blood tests (glucose and A1C) are weighted by blood sample weights,}\\
%		\multicolumn{5}{l}{the others are weighted by individual weights.}\\
%		\multicolumn{5}{l}{Glucose and A1C levels are estimated in subgroups of people without diabetes.}\\
%		\multicolumn{5}{l}{\textsuperscript{*} For continuous variables, the F test was used to determine differences between latent classes}\\   
%		\multicolumn{5}{l}{with Bonferroni correction to account for multiple testing across >2 classes.}\\
%		\multicolumn{5}{l}{For categorical variables, differences between latent classes were assessed}\\
%		\multicolumn{5}{l}{using the adjusted Pearson Chi-2 test for survey data.}\\
%		\multicolumn{5}{l}{\textsuperscript{\dag} Hypertension was defined as either systolic blood pressure $\geqslant$ 140 mmHg or diastolic}\\ 
%		\multicolumn{5}{l}{blood pressure $\geqslant$ 90 mmHg, or under}\\
%		\multicolumn{5}{l}{treatment for hypertension.}\\
%		\multicolumn{5}{l}{\textsuperscript{\ddag} Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake}\\
%		\multicolumn{5}{l}{\textsuperscript{\S} DM was defined by A1C > 6.5\%.}\\
%		\multicolumn{5}{l}{\textsuperscript{\P} Physical activity was calculated as mean time spent at moderate or vigorous physical activity}\\ 
%		\multicolumn{5}{l}{during the survey.}\\
%	\end{tabular}
%\end{table}

\rowcolors{2}{white}{white}

### 2018-08-01 paper/Tables/2by2Table1.Rmd
tables replaced with time slots versions

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_50_paper.csv", header = T)
names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
dt[is.na(dt)] <- ""
# library(formattable)

@@

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_7slots.csv", header = T)
dt <- dt[,-7]
names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
dt[is.na(dt)] <- ""
# library(formattable)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/timeslots_cw3cb3_univariate.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Time slots of the day", "Responses of carbohydrate intake", "Frequency", "Precentages (%)", 
               "Class 1 (30.8%)", "Class 2 (39.8%)", "Class 3 (29.5%)")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Day Level Latent Class Solution for Three-Class Model (No Individual level Model)", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
    add_header_above(c(" ", " ", " ", " ", "High carbohydrate day", "Lower carbohydrate day", "Regular day"))

### 2018-08-01 paper/Tables/2by2Table1.tex
tables replaced with time slots versions

\caption{\label{tab:unnamed-chunk-4}Fit Criteria for Each Model Specification}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{cccccc}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Number of level 1 classes} \\
\cmidrule(l{2pt}r{2pt}){2-7}
Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
\midrule
\showrowcolors
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
\hspace{1em}No. of free parameters & 48 & 97 & 146 & 195 & 244\\
\hspace{1em}\hspace{1em}Log-likelihood & -372017.293 & -368913.708 & -366664.971 & -365528.553 & -364901.166\\
\hspace{1em}\hspace{1em}BIC & 744519.661 & 738807.672 & 734805.379 & 733027.723 & 732268.13\\
\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & --- & < 0.0001 & < 0.0001 & 0.8478 & 0.7602\\
\hspace{1em}\hspace{1em}Entropy & 1 & 0.777 & 0.666 & 0.658 & 0.648\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Random effects model}}\\
\hspace{1em}2 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 195 & 293 & 391 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -363460.153 & -361571.164 & -360297.394 & \\
\hspace{1em}\hspace{1em}BIC &  & 728890.925 & 726103.308 & 724546.13 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.834 & 0.798 & 0.784 & \\
\hspace{1em}3 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 293 & 440 & 587 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -360910.13 & -358902.821 & -357404.521 & \\
\hspace{1em}\hspace{1em}BIC &  & 724781.241 & 722252.166 & 720741.109 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.824 & 0.793 & 0.824 & \\
\hspace{1em}4 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 391 & 587 & 783 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -358684.859 & -356668.354 & -355235.955 & \\
\hspace{1em}\hspace{1em}BIC &  & 720078.473 & 719268.774 & 718384.699 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.816 & 0.817 & 0.806 & \\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:unnamed-chunk-4}Fit Criteria for Each Model Specification}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{cccccc}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Number of level 1 classes} \\
\cmidrule(l{2pt}r{2pt}){2-6}
Model & 1 class & 2 classes & 3 classes & 4 classes & 5 classes\\
\midrule
\showrowcolors
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Fixed effects model}}\\
\hspace{1em}No. of free parameters & 14 & 29 & 44 & 59 & 74\\
\hspace{1em}\hspace{1em}Log-likelihood & -173793.306 & -172669.771 & -172039.204 & -171633.941 & -171377.292\\
\hspace{1em}\hspace{1em}BIC & 347728.092 & 345632.608 & 344523.06 & 343864.121 & 343502.409\\
\hspace{1em}\hspace{1em}Lo-Mendell-Rubun LRT & -- & < 0.0001 & 1e-04 & < 0.0001 & < 0.0001\\
\hspace{1em}\hspace{1em}Entropy & 1 & 0.31 & 0.392 & 0.51 & 0.481\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Random effects model}}\\
\hspace{1em}2 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 59 & 89 & 119 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -169331.132 & -168700.96 & -168366.193 & \\
\hspace{1em}\hspace{1em}BIC &  & 339258.502 & 338301.338 & 337934.968 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.581 & 0.569 & 0.555 & \\
\hspace{1em}3 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 89 & 134 & 179 & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -166936.279 & -166348.815 & -166062.761 & \\
\hspace{1em}\hspace{1em}BIC &  & 334771.968 & 334051.799 & 333934.448 & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.677 & 0.63 & 0.644 & \\
\hspace{1em}4 between classes &  &  &  &  & \\
\hspace{1em}\hspace{1em}No. of free parameters &  & 119 & 179 &  & \\
\hspace{1em}\hspace{1em}Log-likelihood &  & -165441.731 & -164845.696 &  & \\
\hspace{1em}\hspace{1em}BIC &  & 332086.045 & 331500.318 &  & \\
\hspace{1em}\hspace{1em}Entropy &  & 0.729 & 0.659 &  & \\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviation: No, number; BIC, Bayesian information criterion; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.}\\
\end{tabular}
\end{table}

\caption{\label{tab:unnamed-chunk-5}Day Level Latent Class Solution for Three-Class Model (No Individual level Model)}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{lllllll}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{High carbohydrate day} & \multicolumn{1}{c}{Lower carbohydrate day} & \multicolumn{1}{c}{Regular day} \\
\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
Time slots of the day & Responses of carbohydrate intake & Frequency & Precentages (\%) & Class 1 (30.8\%) & Class 2 (39.8\%) & Class 3 (29.5\%)\\
\midrule
\showrowcolors
6 am – 9 am &  &  &  &  &  & \\
 & Not eating & 7655 & 31.2 & 0.129 & 0.45 & 0.32\\
 & Eating, Carbohydrate < 50\% & 4500 & 18.4 & 0.13 & 0.267 & 0.128\\
 & Eating, Carbohydrate >= 50\% & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
9 am – 12 am &  &  &  &  &  & \\
 & Not eating & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
 & Eating, Carbohydrate < 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
 & Eating, Carbohydrate >= 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
12 noon – 2 pm &  &  &  &  &  & \\
 & Not eating & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
 & Eating, Carbohydrate < 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.56\\
 & Eating, Carbohydrate >= 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
2 pm – 5 pm &  &  &  &  &  & \\
 & Not eating & 6926 & 28.3 & 0.13 & 0.123 & 0.659\\
 & Eating, Carbohydrate < 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
 & Eating, Carbohydrate >= 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
5 pm – 8 pm &  &  &  &  &  & \\
 & Not eating & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
 & Eating, Carbohydrate < 50\% & 14240 & 58.2 & 0.516 & 0.59 & 0.639\\
 & Eating, Carbohydrate >= 50\% & 7200 & 29.4 & 0.37 & 0.211 & 0.328\\
8 pm – 10 pm &  &  &  &  &  & \\
 & Not eating & 8722 & 35.6 & 0.322 & 0.291 & 0.48\\
 & Eating, Carbohydrate < 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
 & Eating, Carbohydrate >= 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
10 pm – 6 am &  &  &  &  &  & \\
 & Not eating & 16295 & 66.6 & 0.68 & 0.59 & 0.751\\
 & Eating, Carbohydrate < 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
 & Eating, Carbohydrate >= 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
\bottomrule
\end{tabular}
\end{table}
